---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
** NOTE: This is an untested and poorly documented toy reimplementation of 
[lbozhilova/Kimura-Distribution](https://github.com/lbozhilova/Kimura-Distribution).**

# kimura

<!-- badges: start -->
<!-- badges: end -->

The goal of `kimura` is to fit Kimura distributions to heteroplasmy data and 
test for evidence of selection pressure.

## Installation

You can install the development version of `kimura` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
library("devtools")
devtools::install_github("lbozhilova/kimura")
```

## Example

The principal purpose of this package is to perform hypothesis test for the presence of selection pressure in
mtDNA heteroplasmy distributions (Wonnapinij et al., 2008). This can be done like so:

```{r example, warning=FALSE}
library(kimura)

# Load some heteroplasmy data
h <- c(0.06, 0.08, 0.27, 0.37, 0.40, 0.45, 0.56, 0.61, 0.75, 0.79)

# Carry out test for selection 
test_kimura(h)
```

There is also some additional functionality for generating data from the Kimura distribution.

```{r example2, warning=FALSE}
# Initialise Kimura parameters
p <- 0.6
b <- 0.95

# Probability of allele loss
dkimura(0, p, b)
# Probability of fixing an allele
dkimura(1, p, b)

# Kimura(p, d) CDF at 0.1 intervals
pkimura(seq(0, 1, 0.1), p, b)

# Random number generation
rkimura(10, p, b)
```

## References

Wonnapinij, Passorn, Patrick F. Chinnery, and David C. Samuels. "The distribution of mitochondrial DNA heteroplasmy due to random genetic drift." The American Journal of Human Genetics 83.5 (2008): 582-593.

Kimura, Motoo. "Solution of a process of random genetic drift with a continuous model." Proceedings of the National Academy of Sciences of the United States of America 41.3 (1955): 144.
